Initial Analysis

### 2019-08-28 Initial_Analysis.Rmd
Exploring results per species

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel" # for parallelization
)

@@

# Spatial Data needed to remove duplicates
sau_eez_fes <- read.csv(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))

@@

Clean_Results_Trans <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Model_Index,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(1,2, 
    Neighbor_Territory = FishingRegion,
    Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

# For Carmelia
#Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))

# Load results for non transboundary (discrete) stocks
Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

TenTwenyfive <- Clean_Results %>% 
  filter(#Model_Index == 100,
         Area_Index >= 0.25,
         Area_Index <= 0.75,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory,Model #,Model_Index
           ) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory)),
    Trans_Rate = n_trans/n_countries
    ) #%>% 
  # filter(Model_Index == 100)
  # head(Results_Data)

@@

## Number of transboundary species per country

# Number of Transboundary Species
length(unique(Results_Trans$TaxonKey)) #675 spp

# Number of Discret EEZ species
length(unique(Results_Discrete$TaxonKey))

@@

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  "circlize", # For circular plot
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel", # for parallelization
  "taxize", # For getting species names
  "rfishbase" # for species ecosystem affinity
)

@@

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/exploited_species_list.csv",sep=""))
Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/SppTaxonName.csv",sep=""))

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep=""))

@@

Auto_Remove_Territories <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Model_Index,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(1,2, 
    Neighbor_Territory = FishingRegion,
    Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

#### Manual removal of those left...

# List of territories to eliminate (No other neighobors but mainland)
Islands_to_Remove <- c(
  "Brazil (Fernando de Noronha)",
  "Brazil (St Paul and St. Peter Archipelago)",
  "Hawaii Main Islands (USA)",
  "Hawaii Northwest Islands (USA)",
  "Juan Fernandez Islands (Chile)",
  "Kermadec Isl. (New Zealand)"
)

# Complete list of territories to remove from dataset (Including islands)

Territories_to_Remove <- Results_Trans %>% 
  filter(
    Country_Territory %in% Islands_to_Remove |
      Neighbor_Territory %in% Islands_to_Remove |
      Country_Territory == "Balearic Island (Spain)" & Neighbor_Territory == "Spain (Mediterranean and Gulf of Cadiz)" |
      Country_Territory == "British Virgin Isl. (UK)" & Neighbor_Territory == "Anguilla" |
      Neighbor_Territory == "British Virgin Isl. (UK)" & Country_Territory == "Anguilla" |
      Country_Territory == "Corsica (France)" & Neighbor_Territory == "France (Mediterranean)" |
      Neighbor_Territory == "Corsica (France)" & Country_Territory == "France (Mediterranean)" |
      Country_Territory == "Crete (Greece)" & Neighbor_Territory == "Grece" |
      Neighbor_Territory == "Crete (Greece)" & Country_Territory == "Grece" |
      Country_Territory == "Cyprus (North)" & Neighbor_Territory == "Cyprus (South)" |
      Neighbor_Territory == "Cyprus (North)" & Country_Territory == "Cyprus (South)" |
      Country_Territory == "Channel Isl. (UK)" & Neighbor_Territory == "United Kingdom" |
      Neighbor_Territory == "Channel Isl. (UK)" & Country_Territory == "United Kingdom" |
      Country_Territory == "Glorieuse Islands (France)" & Neighbor_Territory == "Mayotte (France)" |
      Neighbor_Territory == "Glorieuse Islands (France)" & Country_Territory == "Mayotte (France)" |
      Country_Territory == "Guam (USA)" & Neighbor_Territory == "Northern Marianas (USA)" |
      Neighbor_Territory == "Guam (USA)" & Country_Territory == "Northern Marianas (USA)" |
      Country_Territory == "Italy" & Neighbor_Territory == "Sardinia (Italy)" |
      Neighbor_Territory == "Italy" & Country_Territory == "Sardinia (Italy)" |
      Country_Territory == "Italy" & Neighbor_Territory == "Sicily (Italy)" |
      Neighbor_Territory == "Italy" & Country_Territory == "Sicily (Italy)" |
      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (main islands)"|
      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (main islands)"|
      Country_Territory == "Japan (Daito Islands)" & Neighbor_Territory == "Japan (Ogasawara Islands)"|
      Neighbor_Territory == "Japan (Daito Islands)" & Country_Territory == "Japan (Ogasawara Islands)"|
      Country_Territory == "Norway" & Neighbor_Territory == "Svalbard Isl. (Norway)" |
      Neighbor_Territory == "Norway" & Country_Territory == "Svalbard Isl. (Norway)" |
      Country_Territory == "Sicily (Italy)" & Neighbor_Territory == "Sardinia (Italy)" |
      Neighbor_Territory == "Sicily (Italy)" & Country_Territory == "Sardinia (Italy)" |
      Country_Territory == "South Africa (Atlantic Coast)" & Neighbor_Territory == "South Africa (Indian Ocean Coast)" |
      Neighbor_Territory == "South Africa (Atlantic Coast)" & Country_Territory == "South Africa (Indian Ocean Coast)" |
      Country_Territory == "USA (Alaska, Arctic)" & Neighbor_Territory == "USA (Alaska, Subarctic)" |
      Neighbor_Territory == "USA (Alaska, Arctic)" & Country_Territory == "USA (Alaska, Subarctic)"
  ) %>%
  group_by(Country_Territory,Neighbor_Territory) %>% 
  summarise(n())

# Cleaned results 
Clean_Results_Trans <- Auto_Remove_Territories %>% 
  anti_join(Territories_to_Remove,
            by = c("Country_Territory","Neighbor_Territory")
  ) %>% 
  filter(Same_Nation == "No")

# For Carmelia
# Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))

# Load results for non transboundary (discrete) stocks
# Results_Discrete <- fread(paste(Results_Path,"Non_Transboundary_Data.csv",sep=""))

@@

#### Determine transboundary stocks and countries based on selected trsholds ####

#### Select Tresholds ###

# Area Index
Min_AI <- 0.25 # Min area index
Max_AI <- 1-Min_AI # Max Area Index

# Model Index
MI <- 100 # Model Index

####_____End Select Tresholds_______ ###

#### Determine transboundary and non-transboundary species and nations

TenTwenyfive <- Clean_Results_Trans %>% 
  filter(
         Area_Index >= Min_AI,
         Area_Index <= Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory)),
    Trans_Rate = n_trans/n_countries
    )
  # filter(Model_Index == 100)
  # head(Results_Data)

### Non-transboundary

Non_trans_Area_TenTwenyfive <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(Name=Country_Territory) %>% 
  summarise(
    n_no_trans = length(unique(TaxonKey)),
    n_countries = length(unique(Neighbor_Territory))
  )

@@

## Analysis per Country

@@

## Analysis per Species

# Number of Transboundary Species
length(unique(Clean_Results_Trans$TaxonKey)) #664 spp

# Number of Discret EEZ species

# Ge those stocks that are not trans due to Area_Index
length(unique(Results_Discrete$TaxonKey))

```{n_species_country, eval =F, echo =F}

# Number of countries shared by each Species
Species_Trans <- Clean_Results_Trans %>% 
  filter(
         Area_Index < Min_AI |
         Area_Index > Max_AI,
         Model_Index == MI,
         Same_Nation == "No"
         ) %>% 
  group_by(TaxonKey) %>% 
  summarise(
    n_countries = length(unique(Country_Territory))
  ) %>% 
  left_join(Exploited_Species) %>%
  left_join(Spp_Clasification)

hist(Species_Trans$n_countries)

# use taxize to get species family name

Species_family_list <- Species_Trans %>% 
  mutate(scientific_name = paste(Genus,Species)) %>% 
  pull(scientific_name) %>% 
  tax_name(Species_list, get = "family", db = 'itis')

# Use rfishbase to get species environment

Species_list <- Species_Trans %>% 
  mutate(scientific_name = paste(Genus,Species)) %>% 
  pull(scientific_name)

Species_environ_list <- rbind(species(Species_list, 
                                      fields = species_fields$habitat[4])
                              ) %>% 
  mutate(scientific_name = Species_list)

```{n_species_barplot, eval =F, echo =F}

Species_Trans %>% 
  group_by(Genus,DemPel) %>% 
  summarise(Countries_Genus = sum(n_countries,na.rm=T)) %>% 
  mutate(Bins = cut(Countries_Genus, breaks = 5)) %>% 
  filter(Countries_Genus < 200,
         !is.na(DemPel)) %>%
  ggplot(.,
       aes(
         x = reorder(Genus,Countries_Genus),
         y = Countries_Genus,
         fill = Countries_Genus,
         colour = Countries_Genus
       )
       ) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme(axis.text.y = element_text(size = 5,
                               angle = 0,
                               face = "italic")
        ) +
  facet_wrap(~DemPel,
             scales = "free")
